---
title:
author: 
date: 
output: revealjs::revealjs_presentation
css: docs/styles.css
incremental: true
slideNumber: true
highlight: pygments
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A/B Testing: Experimental Design  {data-background="art.jpg" .title}
March 26, 2019

## Variables

> - <b>Question</b>: Will making a colour change to my website result in more button clicks?
> - <b>Hypothesis</b>: By changing the colour to 'blue' will result in more button clicks. 
> - <b>Dependent Variable</b>: Clicked the button or not.
> - <b>Independent Variable</b>: Header colour.

## Evaluate Preliminary Dataset

```{r clicks, message=FALSE, warning=FALSE}
library(tidyverse)

clicks <- read.csv("click.csv")
clicks
```

## Calculate Conversion Rate
Calculate the conversion rate by using the 'dplyr' function <b>summarize</b> to find the means of the clicks.
```{r}
library(dplyr)
clicks <- read.csv("click.csv")

clicks %>%
  summarize(conversion_rate = mean(clicked_button))
```

## Factors
We computed the rate over the year, but there could be other factors that affect the number of clicks. We'll compute the conversion rate of clicks by month to see if there is a change month to month. 

```{r message=FALSE, warning=FALSE}
library(lubridate)

clicks %>%
  group_by(month(visit_date)) %>%
  summarize(conversion_rate = mean(clicked_button))
```

## Plot the Results
```{r message=FALSE, warning=FALSE}
library(ggplot2)

clicks_sum <- clicks %>%
  group_by(month(visit_date)) %>%
  summarize(conversion_rate = mean(clicked_button))

clicks_sum_plot <- ggplot(clicks_sum, aes(x = `month(visit_date)`, y = conversion_rate)) + 
  geom_point() + 
  geom_line()
```

## View Plot

```{r echo==FALSE, fig.height=5}
plot(clicks_sum_plot)
```

## Power Analysis
A/B testing tries to run both conditions simultaneously as opposed to separately so that both are exposed to the same variables. 

A power analysis will tell you how many data points (or sample size) you’ll need to ensure the effect is real.

> - <b>Statistical Test</b>: Test you plan to run
> - <b>Baseline Value</b>: Value for the current condition
> - <b>Desired Value</b>: Expected value for the test condition
> - <b>B</b>: Proportion of the data (ideally 0.5)
> - <b>Alpha</b>: Level where effect is significant (generally 0.05)
> - <b>Power</b>: Probability rejecting the null hypothesis (generally 0.8)

## Running a Power Analysis
```{r message=FALSE, warning=FALSE}
library(powerMediation)

total_sample_size <- SSizeLogisticBin(p1 = 0.2,
                                      p2 = 0.3,
                                      B = 0.5,
                                      alpha = 0.05,
                                      power= 0.8)

total_sample_size
```

## Experiment Results
